Towards a Wide-Coverage Grammar

### 2013-06-24 slides/presentation.tex
Typos

  Requirements for building a wide-coverage grammar:
    \begin{itemize}
    \item Having linguistic resources to build upon
      \begin{itemize}
      \item Frilex, a formalism-independent lexical database
      \item Frigram, a French interaction grammar
      \end{itemize}
    \item Debugging the grammar
      \begin{itemize}
        \item A toolkit for formulating ACGs as simple metagrammars, for
          examining how they work and for checking their consistency.
      \end{itemize}
    \item Using a formalism that allows for a simple grammar
      \begin{itemize}
      \item The need to express multiple independent constraints led us
        to graphical abstact categorial grammars.
      \end{itemize}
    \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item ACGs are based on types (IILL formulas).
  \item IGs are based on polarized tree descriptons.
  \item Perrier has linked the two.

>>>>

  Requirements for building a wide-coverage grammar:
    \begin{itemize}
    \item Having linguistic resources to build upon
      \begin{itemize}
      \item Frilex, a formalism-independent lexical database
      \item Frigram, a French interaction grammar
      \end{itemize}
    \item Debugging the grammar
      \begin{itemize}
        \item A toolkit for formulating ACGs as simple metagrammars, for
          examining how they work and for checking their consistency.
      \end{itemize}
    \item Using a formalism that allows for a simple grammar
      \begin{itemize}
      \item The need to express multiple independent constraints led us
        to graphical abstract categorial grammars.
      \end{itemize}
    \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item ACGs are based on types (IILL formulas).
  \item IGs are based on polarized tree descriptions.
  \item Perrier has linked the two.
